---
title: "RepResearchProject1"
output: html_document
---

The below code loads the data and pre-processes it into organized data

```{r}
filename <- ""
data <- read.csv(filename,header = TRUE)

```

The below code displays the histogram of total number of steps taken by day followed by the mean and median of steps taken per day

```{r}

hist(x = sum(dailysteps, na.rm = TRUE))

meandailysteps <- mean(sum(dailysteps, na.rm = TRUE))
mediandailysteps <- median(sum(dailysteps, na.rm = TRUE))

paste("The mean of the daily steps is "&$mean&". The median of the daily steps is "&$median&".")
```

This code calculates the average daily activity pattern. By creating a time series plot of the 5 minute intervals and the average number of steps taken across all days. It lists the 5 minute interval that on average, across the days, in the data contains the maximum number of steps(ie 9 to 905 across all days was most active interval). 

```{r}

```

This code imputs the missing values into the dataset. It does this by substituting the missing values with the mean of that day of intervals. It then creates a new dataset with the NAs filled in and a similar histogram of the total steps taken each day adn reports the mean and median after the numbers have been updated.

```{r}

```

This code differentiates etween weekdays and weekends and reports the mean and median for each subset.

```{r}
#use weekdays()
```






